14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-05-11 rules/rules19.tex
Rules: Add link for benchmark selection script

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
the \challtrack, the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The organizers will remove all
  benchmarks that were solved by all solvers (including non-competitive
  solvers) in less than one second in 2018.
\item \emph{\ucoretrack.} In addition, for the \ucoretrack, all
  benchmarks with a single assertion will be removed.
\item \emph{Cap the number of instances in a division.} The organizers will
  limit the number of benchmarks in a division based on the size of the
  corresponding logic in SMT-LIB as follows:
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} If a logic contains less than 300 instances,
      all instances will selected.
  \item \label{bench-sel-600} If a logic contains between 300 and 600
    instances, a subset of 300 instances from the set will be selected.
  \item \label{bench-sel-more} If a logic contains more than 600 instances,
    50\% of the benchmarks will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at \rem{link tba} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.

>>>>

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
the \challtrack, the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The organizers will remove all
  benchmarks that were solved by all solvers (including non-competitive
  solvers) in less than one second in 2018.
\item \emph{\ucoretrack.} In addition, for the \ucoretrack, all
  benchmarks with a single assertion will be removed.
\item \emph{Cap the number of instances in a division.} The organizers will
  limit the number of benchmarks in a division based on the size of the
  corresponding logic in SMT-LIB as follows:
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} If a logic contains less than 300 instances,
      all instances will selected.
  \item \label{bench-sel-600} If a logic contains between 300 and 600
    instances, a subset of 300 instances from the set will be selected.
  \item \label{bench-sel-more} If a logic contains more than 600 instances,
    50\% of the benchmarks will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at
\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.
